Fitness effects of mutations to SARS-CoV-2 proteins

### 2023-01-15 paper/paper.tex
update corr figure

\begin{figure*}
\includegraphics[width=\linewidth]{figs/fig2.pdf}
\caption{
Distribution of effects of different types of mutations.
{\bf (A)}
Histograms of effects of synonymous, nonsynonymous, and stop-codon mutations across all viral genes.
Neutral mutations have effects of zero (dashed gray vertical lines), and deleterious mutations have negative effects.
{\bf (B)}
Effects of each type of mutation for each viral gene.
Dark squares indicate the median effect, and the lighter rectangles span the interquartile range.
Mutation types are color-coded as in panel A.
Both panels show only mutations with expected counts of at least 10.
See \url{https://jbloomlab.github.io/SARS2-mut-fitness/effects_histogram.html} and \url{https://jbloomlab.github.io/SARS2-mut-fitness/effects_dist.html} for interactive versions of these plots that allow adjustment of the expected-count cutoff and other options (such as separate histograms for each gene).
\label{fig:effects_dist}
}
\end{figure*}

\begin{figure*}
\centering
{\bf \Large A \hspace{0.32\linewidth} B \hspace{0.32\linewidth}}

\includegraphics[width=0.32\linewidth]{figs/clade_corr_chart.pdf}
\hspace{0.05\linewidth}
\includegraphics[width=0.32\linewidth]{figs/subset_corr_chart.pdf}
\caption{
Correlations between amino-acid fitness estimates made using different sequence subsets.
{\bf (A)} Estimates made using only sequences from the Omicron BA.2 clade or only the Alpha clade, or {\bf (B)} estimates made using only sequences from the USA or England.
In the scatter plots, each point is a different amino-acid mutation, and the orange text at upper left shows the number of mutations and Pearson correlation coefficient.
Both panels show only mutations with expected counts of at least 20.
For interactive versions of these plots that show correlations among estimates from all clade pairs, allow adjustment of the expected-count cutoff, and allow examination of correlations for just specific genes, see \url{https://jbloomlab.github.io/SARS2-mut-fitness/clade_corr_chart.html} and \url{https://jbloomlab.github.io/SARS2-mut-fitness/subset_corr_chart.html}.
\label{fig:corr}
}
\end{figure*}

>>>>

\begin{figure*}
\includegraphics[width=\linewidth]{figs/dist.pdf}
\caption{
Distribution of effects of different types of mutations.
{\bf (A)}
Histograms of effects of synonymous, nonsynonymous, and stop-codon mutations across all viral genes.
Neutral mutations have effects of zero (dashed gray vertical lines), and deleterious mutations have negative effects.
{\bf (B)}
Effects of each type of mutation for each viral gene.
Dark squares indicate the median effect, and the lighter rectangles span the interquartile range.
Mutation types are color-coded as in panel A.
Both panels show only mutations with expected counts of at least 10.
See \url{https://jbloomlab.github.io/SARS2-mut-fitness/effects_histogram.html} and \url{https://jbloomlab.github.io/SARS2-mut-fitness/effects_dist.html} for interactive versions of these plots that allow adjustment of the expected-count cutoff and other options (such as separate histograms for each gene).
\label{fig:dist}
}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figs/corr.png}
\caption{
Correlations between amino-acid fitness estimates made using different sequence subsets.
{\bf (A)} Estimates made using only sequences from the indicated viral clades, or {\bf (B)} estimates made using only sequences from the USA or England.
Each point is a different amino-acid mutation, and the orange text at upper left shows the number of mutations and Pearson correlation coefficient.
Both panels show only mutations with expected counts of at least 10 in each subset of sequences.
See \url{https://jbloomlab.github.io/SARS2-mut-fitness/clade_corr_chart.html} and \url{https://jbloomlab.github.io/SARS2-mut-fitness/subset_corr_chart.html}.For interactive versions of these plots that show correlations among additional clade pairs, allow adjustment of the expected-count cutoff, and allow examination of mutations for just specific genes.
\label{fig:corr}
}
\end{figure*}
